A Fast and Tight Heuristic for A* in Road Networks

### 2021-01-29 paper/ch_potentials.tex
suggestions for fixes of the things I commented on

\section{Introduction}
\label{sec:intro}
The past decade has seen a plethora of research on route planning in large street networks~\cite{bdgmpsww-rptn-16}.
Routing a user through a road network can be formalized as the shortest path problem in weighted graphs.
Nodes represent intersections.
Roads are modeled using edges.
Edges are weighted by their traversal times.
The problem can be solved with Dijkstra's algorithm~\cite{d-ntpcg-59}.
Unfortunately, on continental sized networks, it is too slow for many applications.
Thus, speed-up techniques have been developed.
One popular example are Contraction Hierarchies~(CH)~\cite{gssv-erlrn-12}.
They have been used successfully in many real world applications.
A CH exploits the inherent hierarchy of road networks.
In a preprocessing step, additional shortcut edges are inserted, which allow skipping unimportant parts of the network at query time.
Another popular example is Multi-Level-Dijkstra~(MLD)~\cite{swz-umlgt-02} also known as CRP~\cite{dgpw-crprn-13}.
It is also used in practice~\cite{bingblog}.
MLD also uses shortcut edges.
% ich haette das at least eigentlich schon gerne drin. CH erreicht wesentlich mehr als 3 groessenordnungen
Both approaches achieve speed-ups of three orders of magnitude over Dijkstra's algorithm.

@@

Truck routing differs from car routing due to night driving bans and other restrictions.
In~\cite{kswz-erptd-p-20}, a preliminary version of CH-Potentials\footnote{
In~\cite{kswz-erptd-p-20}, CH-Potentials are used as a blackbox referring to an early ArXiv preprint~\cite{strasser2019perfect} of ours.
Our submitted paper is the finished version of the ArXiv preprint.
% der punkt macht fuer mich keinen Sinn.
% Dass wir keine der Contributions von kswz-erptd-p-20 beschreiben ist ja offensichtlich, sieht ja jeder in dem Abschnitt.
% Wichtiger finde ich, dass kswz-erptd-p-20 nix von uns beschreibt.
% Das meinte ich zumindest mit dem Satz den du geloescht hast.
% Aber der jetzt folgende Satz sagt nur, dass unser paper hier nix von kswz-erptd-p-20 beschreibt.
The submitted paper does not describe any of the contribution of \cite{kswz-erptd-p-20}.
} is used for such a scenario.
The work considers time-dependent blocked edges and waiting at parking locations.
Further, a trade-off between arrival time and route quality is considered.

>>>>

\section{Introduction}
\label{sec:intro}
The past decade has seen a plethora of research on route planning in large street networks~\cite{bdgmpsww-rptn-16}.
Routing a user through a road network can be formalized as the shortest path problem in weighted graphs.
Nodes represent intersections.
Roads are modeled using edges.
Edges are weighted by their traversal times.
The problem can be solved with Dijkstra's algorithm~\cite{d-ntpcg-59}.
Unfortunately, on continental sized networks, it is too slow for many applications.
Thus, speed-up techniques have been developed.
One popular example are Contraction Hierarchies~(CH)~\cite{gssv-erlrn-12}.
They have been used successfully in many real world applications.
A CH exploits the inherent hierarchy of road networks.
In a preprocessing step, additional shortcut edges are inserted, which allow skipping unimportant parts of the network at query time.
Another popular example is Multi-Level-Dijkstra~(MLD)~\cite{swz-umlgt-02} also known as CRP~\cite{dgpw-crprn-13}.
It is also used in practice~\cite{bingblog}.
MLD also uses shortcut edges.
% ich haette das at least eigentlich schon gerne drin. CH erreicht wesentlich mehr als 3 groessenordnungen
Both approaches achieve speed-ups of at least three orders of magnitude over Dijkstra's algorithm.

@@

Truck routing differs from car routing due to night driving bans and other restrictions.
In~\cite{kswz-erptd-p-20}, a preliminary version of CH-Potentials\footnote{
In~\cite{kswz-erptd-p-20}, CH-Potentials are used as a blackbox referring to an early ArXiv preprint~\cite{strasser2019perfect} of ours.
Our submitted paper is the finished version of the ArXiv preprint.
% der punkt macht fuer mich keinen Sinn.
% Dass wir keine der Contributions von kswz-erptd-p-20 beschreiben ist ja offensichtlich, sieht ja jeder in dem Abschnitt.
% Wichtiger finde ich, dass kswz-erptd-p-20 nix von uns beschreibt.
% Das meinte ich zumindest mit dem Satz den du geloescht hast.
% Aber der jetzt folgende Satz sagt nur, dass unser paper hier nix von kswz-erptd-p-20 beschreibt.
\cite{kswz-erptd-p-20} does not describe any of the contribution of this paper.
} is used for such a scenario.
The work considers time-dependent blocked edges and waiting at parking locations.
Further, a trade-off between arrival time and route quality is considered.
